---
title: "Rep_Table4a"
author: "Bradley Paye"
date: "2025-02-12"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This document loads data from Paye and Timmermann (2006, Journal of Empirical Finance). It then replicates the univariate (full sample) regressions reported in Table 4, panel A of the paper.


```{r loaddata}
library(here)  
library(readxl)

#Load 1952-2003 data for multiple countries
Data_intl52 <- read_excel(here("RawData", "IntlData1952.xlsx"))
 
Data_intl52

#Load 1970-2003 data for US,UK
Data_intl70 <- read_excel(here("RawData", "IntlData1970.xlsx"))

summary(Data_intl70)

```
## Run a first regression

Here we will try a first regression, replicating entry for S&P 500 excess return on DY in Table 4 panel A.

From the table, the R^2^ is 0.62 percent and the slope is 0.32.

```{r firstreg}
library(dplyr)
library(tibble)
#create lagged predictors (if not already included)
regdata <- Data_intl52 %>% add_column(lagUS_DY = lag(Data_intl52$USDY)/100, lagUS_TB = lag(Data_intl52$USTB)/1200,
        lagUK_TB = lag(Data_intl52$UKTB)/1200, 
        lagUK_Term = lag(Data_intl52$UKTerm)/1200)

#Now regress S&P 500 excess return (USeret) on lagged DY
lm_USdy <- lm(USeret ~ lagUS_DY,data=regdata)

summary(lm_USdy)


```
## Make table replicating top of Table 4, panel A

Now we will run the full set of predictive regressions for the US data over 1952-2003.

```{r toptable4}

#Additional DY regressions
lm_Nysedy <- lm(NYSEeret ~ lagUS_DY,data=regdata)
lm_Nandy <- lm(NANeret ~ lagUS_DY,data=regdata)
lm_UKdy <- lm(UKeret ~ lagUK_DY, data=regdata)

#T-bill regressions
lm_Nysetb <- lm(NYSEeret ~ lagUS_TB,data=regdata)
lm_Nantb <- lm(NANeret ~ lagUS_TB,data=regdata)
lm_UStb <- lm(USeret ~ lagUS_TB,data=regdata)
lm_UKtb <- lm(UKeret ~ lagUK_TB,data=regdata)

#Term spread regressions
lm_Nyseterm <- lm(NYSEeret ~ lagUS_Term,data=regdata)
lm_Nanterm <- lm(NANeret ~ lagUS_Term,data=regdata)
lm_USterm <- lm(USeret ~ lagUS_Term,data=regdata)
lm_UKterm <- lm(UKeret ~ lagUK_Term,data=regdata)

#def spread regressions -- note we always us US DEF spread
lm_Nysedef <- lm(NYSEeret ~ lagUS_DEF, data=regdata)
lm_Nandef <- lm(NANeret ~ lagUS_DEF,data=regdata)
lm_USdef <- lm(USeret ~ lagUS_DEF,data=regdata)
lm_UKdef <- lm(UKeret ~ lagUS_DEF,data=regdata)

summary(lm_Nysedy)
summary(lm_Nandy)

# Next part makes dataframe / table
columns= c("DY_r2","DY_beta","DY_se",
           "TBL_r2","TBL_beta","TBL_se",
           "TERM_r2","TERM_beta","TERM_se",
           "DEF_r2","DEF_beta","DEF_se") 

Tab4_Top = data.frame(matrix(nrow = 0, ncol = length(columns))) 
# assign column names
colnames(Tab4_Top) = columns

# assign reg results
tmp <- sqrt(diag(vcov(lm_Nysedy)))
Tab4_Top[1,2] <- lm_Nysedy$coefficients[2]
Tab4_Top[1,1] <- summary(lm_Nysedy)$r.squared*100
Tab4_Top[1,3] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nandy)))
Tab4_Top[2,2] <- lm_Nandy$coefficients[2]
Tab4_Top[2,1] <- summary(lm_Nandy)$r.squared*100
Tab4_Top[2,3] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_USdy)))
Tab4_Top[3,2] <- lm_USdy$coefficients[2]
Tab4_Top[3,1] <- summary(lm_USdy)$r.squared*100
Tab4_Top[3,3] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_UKdy)))
Tab4_Top[4,2] <- lm_UKdy$coefficients[2]
Tab4_Top[4,1] <- summary(lm_UKdy)$r.squared*100
Tab4_Top[4,3] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_UStb)))
Tab4_Top[3,5] <- lm_UStb$coefficients[2]
Tab4_Top[3,4] <- summary(lm_UStb)$r.squared*100
Tab4_Top[3,6] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nysetb)))
Tab4_Top[1,5] <- lm_Nysetb$coefficients[2]
Tab4_Top[1,4] <- summary(lm_Nysetb)$r.squared*100
Tab4_Top[1,6] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nantb)))
Tab4_Top[2,5] <- lm_Nantb$coefficients[2]
Tab4_Top[2,4] <- summary(lm_Nantb)$r.squared*100
Tab4_Top[2,6] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_UKtb)))
Tab4_Top[4,5] <- lm_UKtb$coefficients[2]
Tab4_Top[4,4] <- summary(lm_UKtb)$r.squared*100
Tab4_Top[4,6] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nyseterm)))
Tab4_Top[1,8] <- lm_Nyseterm$coefficients[2]
Tab4_Top[1,7] <- summary(lm_Nyseterm)$r.squared*100
Tab4_Top[1,9] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nanterm)))
Tab4_Top[2,8] <- lm_Nanterm$coefficients[2]
Tab4_Top[2,7] <- summary(lm_Nanterm)$r.squared*100
Tab4_Top[2,9] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_USterm)))
Tab4_Top[3,8] <- lm_USterm$coefficients[2]
Tab4_Top[3,7] <- summary(lm_USterm)$r.squared*100
Tab4_Top[3,9] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_UKterm)))
Tab4_Top[4,8] <- lm_UKterm$coefficients[2]
Tab4_Top[4,7] <- summary(lm_UKterm)$r.squared*100
Tab4_Top[4,9] <- tmp[2]


tmp <- sqrt(diag(vcov(lm_Nysedef)))
Tab4_Top[1,11] <- lm_Nysedef$coefficients[2]
Tab4_Top[1,10] <- summary(lm_Nysedef)$r.squared*100
Tab4_Top[1,12] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_Nandef)))
Tab4_Top[2,11] <- lm_Nandef$coefficients[2]
Tab4_Top[2,10] <- summary(lm_Nandef)$r.squared*100
Tab4_Top[2,12] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_USdef)))
Tab4_Top[3,11] <- lm_USdef$coefficients[2]
Tab4_Top[3,10] <- summary(lm_USdef)$r.squared*100
Tab4_Top[3,12] <- tmp[2]

tmp <- sqrt(diag(vcov(lm_UKdef)))
Tab4_Top[4,11] <- lm_UKdef$coefficients[2]
Tab4_Top[4,10] <- summary(lm_UKdef)$r.squared*100
Tab4_Top[4,12] <- tmp[2]
# display
print(Tab4_Top)

#set row names
row.names(Tab4_Top) <- c("Nyse","Nan","SP500","UK")

knitr::kable(Tab4_Top,digits=3,caption = "Table 4, Panel A (Top)")


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
